---
title: "Evolution of aging"
author: "Roy Moger-Reischer and Jay T. Lennon"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - \usepackage{array}
output: pdf_document
geometry: margin=2.54cm
---

## Clear workspace and set directory

```{r setup}
rm(list=ls())
getwd()
setwd("~/GitHub/XevoLong")
```

## Load packages and functions
```{r}
require("png")
require("dplyr")
require("grid")
require("ggplot")
require("tidyverse")
require("ggpubr")
require("Hmisc")
require("ggrepel")
LL.95 <- function(x) t.test(x)$conf.int[1]
UL.95 <- function(x) t.test(x)$conf.int[2]
sem <- function(x) sqrt(var(x)/length(x))
theme_set(
  theme_bw()
)
```

# Load and process data
```{r}

mydf_raw <- read_csv("~/GitHub/XevoLong/data/cases_lifespan.mutants_jtl.csv")
mydf <- as_tibble(mydf_raw)

mydf$Selection <- factor(mydf$selection, levels = c("NL","L","Anc"))
mydf$Strain_factor<-factor(mydf$strain, levels=c("2","4","5","9","11","16","19","0"))

#mydf$Strain<-recode(mydf$Strain_factor, "2" = "rpl19aΔ", "4" = "pmr1Δ", "5" = "sch9Δ",
#          "9"="ypt6Δ","11"="tor1Δ","16"="tif2Δ","19"="LYS2", "0"="WT")

#mydf$Strain<-factor(mydf$Strain, levels=c("rpl19aΔ","pmr1Δ","sch9Δ","ypt6Δ","tor1Δ","tif2Δ","LYS2","WT"))
mydf$Strain <- factor(mydf$strain, levels=c("rpl19a","pmr1","sch9","ypt6","tor1","tif2","LYS2","WT"))
#mycols<-c("black","black")


avgdf_raw <- read_csv("~/GitHub/XevoLong/data/cases_lifespan.mutants_avgs_jtl.csv")
avgdf <- as_tibble(avgdf_raw)
avgdf$selection <- factor(avgdf$selection, levels = c("NL","L","Anc"))
avgdf$strain_factor <- factor(avgdf$strain, levels=c("2","4","5","9","11","16","19","0"))
#avgdf$Strain <- recode(avgdf$strain_factor, "2" = "rpl19aΔ", "4" = "pmr1Δ", "5" = "sch9Δ", 
#                     "9"="ypt6Δ","11"="tor1Δ","16"="tif2Δ","19"="LYS2", "0"="WT")
avgdf$strain <- recode(avgdf$strain_factor, "2" = "rpl19a", "4" = "pmr1", "5" = "sch9", 
              "9"="ypt6","11"="tor1","16"="tif2","19"="LYS2", "0"="WT")
avgdf$Strain<-factor(avgdf$strain, levels = c("rpl19a","pmr1","sch9","ypt6","tor1","tif2","LYS2","WT"))


ance0df <- read_csv("~/GitHub/XevoLong/data/cases_anc.ANOVA_e0_jtl.csv")
ance0df$strain_factor <- factor(ance0df$strain, levels=c("2","4","5","9","11","16","19","0"))
ance0df$strain <- recode(ance0df$strain_factor, "2" = "rpl19a", "4" = "pmr1", "5" = "sch9",
            "9"="ypt6","11"="tor1","16"="tif2","19"="LYS2", "0"="WT")
ance0df$strain<-factor(ance0df$strain, levels=c("rpl19a","pmr1","sch9","ypt6","tor1","tif2","LYS2","WT"))

ancrrdf<-read_csv("~/GitHub/XevoLong/data/cases_anc.ANOVA_rr.csv")
ancrrdf$Strain_factor<-factor(ancrrdf$Strain, levels=c("2","4","5","9","11","16","19","0"))
ancrrdf$Strain<-recode(ancrrdf$Strain_factor, "2" = "rpl19a", "4" = "pmr1", "5" = "sch9",
              "9"="ypt6","11"="tor1","16"="tif2","19"="LYS2", "0"="WT")
ancrrdf$Strain<-factor(ancrrdf$Strain, levels=c("rpl19a","pmr1","sch9","ypt6","tor1","tif2","LYS2","WT"))
```


# Lifespan
```{r}
myydf_full <- as_tibble(mydf)

#convert reproductive rate from per hour to per day
myydf_full$off.per.hr_50.50 <- myydf_full$off.per.hr_50.50*24

#myydf_full$genotype <- as.factor(myydf_full$genotype)

# lifespan data for NL treatment
ls.NL.ind <- filter(myydf_full, selection == c("NL")) 
ls.NL <- ls.NL.ind  %>%  
  group_by(genotype = fct_inorder(genotype)) %>%
   dplyr::summarise(mean = mean(e0), sem = sem(e0))

# lifespan data for NL treatment
ls.L.ind <- filter(myydf_full, selection == c("L")) 
ls.L <- ls.L.ind  %>%  
  group_by(genotype = fct_inorder(genotype)) %>%
   dplyr::summarise(mean = mean(e0), sem = sem(e0))

# lifespan data for ancestors
ls.A.ind <- filter(myydf_full, selection == c("Anc")) 
ls.A <- ls.A.ind  %>%  
  group_by(genotype = fct_inorder(genotype)) %>%
   dplyr::summarise(mean = mean(e0), sem = sem(e0))

## Make figure

# Create x-axis values
x.ind <- c(rep(1,5), rep(3,5), rep(5,5), rep(7,5), 
        rep(9,5), rep(11,5), rep(13,5), rep(15,5))
x <- c(1, 3, 5, 7, 9, 11, 13, 15)

png(filename="~/GitHub/XevoLong/figures/Fig1.png",
    width = 1200, height = 900, res = 96*2)

plot.new()
par(mar = c(7, 7, 5, 7))

plot(jitter(x.ind, amount = 0.5), ls.NL.ind$e0, xlim = c(0, 16),
     ylim = c(-1, 21), type = "p", pch = 22, bg = "lightblue", 
     col = "lightblue", cex = 0.75, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, lwd = 2, yaxt = "n", xaxt = "n")
box(lwd = 2)

points(jitter(x.ind, amount = 0.5), ls.L.ind$e0,
       pch = 22, bg = "pink", col = "pink", lwd = 2, cex = 0.75)

# Add treatment means
points(x, ls.NL$mean, pch = 22, 
      bg = "blue", col = "blue", lwd = 1.25, cex = 2)

points(x, ls.L$mean, pch = 22, 
      bg = "red", col = "red", lwd = 1.25, cex = 2)

# Add error bars
arrows(x0 = x, y0 = ls.NL$mean, 
       y1 = ls.NL$mean + ls.NL$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "blue")

arrows(x0 = x, y0 = ls.NL$mean, 
       y1 = ls.NL$mean - ls.NL$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "blue")

arrows(x0 = x, y0 = ls.L$mean, 
       y1 = ls.L$mean + ls.L$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "red")

arrows(x0 = x, y0 = ls.L$mean, 
       y1 =ls.L$mean - ls.L$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "red")

# Add ancestors means 
segments(x0 = 0.2, y0 = ls.A$mean[1], x1 = 1.8, y1 = ls.A$mean[1], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 2.2, y0 = ls.A$mean[2], x1 = 3.8, y1 = ls.A$mean[2], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 4.2, y0 = ls.A$mean[3], x1 = 5.8, y1 = ls.A$mean[3], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 6.2, y0 = ls.A$mean[4], x1 = 7.8, y1 = ls.A$mean[4], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 8.2, y0 = ls.A$mean[5], x1 = 9.8, y1 = ls.A$mean[5], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 10.2, y0 = ls.A$mean[6], x1 = 11.8, y1 = ls.A$mean[6], col = "black", lty = 3, lwd = 2.5)
segments(x0 = 12.2, y0 = ls.A$mean[7], x1 = 13.8, y1 = ls.A$mean[7], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 14.2, y0 = ls.A$mean[8], x1 = 15.8, y1 = ls.A$mean[8], col = "black", lty = 3, lwd = 2.5) 

# Add ticks
axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1,
     at = c(1, 3, 5, 7, 9, 11, 13, 15), labels = F)
axis(side = 3, lwd.ticks = 2, cex.axis = 1.25, las = 1,
     at=c(1, 3, 5, 7, 9, 11, 13, 15), labels = F)
axis(side = 2, lwd.ticks = 2, cex.axis = 1.25, las = 1,
    labels = c("0", "5", "10", "15", "20"), at = c(0, 5, 10, 15, 20))
axis(side = 4, lwd.ticks = 2, cex.axis = 1.25, las = 1,
     at=c(0, 5, 10, 15, 20), labels = F)

# Add axis labels
mtext(expression('Strains'), side = 1,
      outer = TRUE, cex = 1.5, line = -2.5, adj = 0.5)

mtext(expression('Life expectancy (d)'), side = 2,
      outer = TRUE, cex = 1.5, line = -4, adj = 0.6)

# Add legend

legend(0.1, 21, legend=c("no longevity", "longevity"),
       col=c("blue", "red"), pt.bg = c("blue", "red"),
       pch = c(22, 22), pt.cex = 1.5, cex = 1, bty = "n")

# Add strain labels
text(x=0.38, y=-7.5,"wild type",srt = 60, xpd = NA, cex = 1)
text(x=2.4, y= -7, expression(paste("rpl10a",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=4.4, y= -7, expression(paste("pmr1",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=6.4, y= -7, expression(paste("sch9",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=8.4, y= -7, expression(paste("ypt6",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=10.4, y= -7, expression(paste("tor1",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=12.4, y= -7, expression(paste("tif2",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=14.4, y= -7, "LYS2", srt = 60, xpd = NA, cex = 1)

# Close Plot Device
dev.off()
graphics.off()

# Show Plot
img <- readPNG("~/GitHub/XevoLong/figures/Fig1.png")

grid.raster(img)

# Statistics

fit.ls <- aov(e0 ~ genotype * selection, data = myydf_full)
summary(fit.ls)

#                   Df Sum Sq Mean Sq F value   Pr(>F)    
# genotype            7  210.8   30.12  10.126 1.86e-08 ***
# selection           2  287.8  143.89  48.374 1.59e-13 ***
# genotype:selection 14   96.5    6.89   2.317   0.0119 *  
# Residuals          64  190.4    2.97    


# Effect of longevity treatment: increased life expectancy by 3.71 d or 120%
long.effect <- myydf_full %>%  
  group_by(selection) %>%
   dplyr::summarise(mean = mean(e0), sem = sem(e0))
```

# Reproduction
```{r}
#myydf_full$genotype <- as.factor(myydf_full$genotype)

# lifespan data for NL treatment
repo.NL.ind <- filter(myydf_full, selection == c("NL")) 
repo.NL <- repo.NL.ind  %>%  
  group_by(genotype = fct_inorder(genotype)) %>%
   dplyr::summarise(mean = mean(off.per.hr_50.50), sem = sem(off.per.hr_50.50))

# lifespan data for NL treatment
repo.L.ind <- filter(myydf_full, selection == c("L")) 
repo.L <- repo.L.ind  %>%  
  group_by(genotype = fct_inorder(genotype)) %>%
   dplyr::summarise(mean = mean(off.per.hr_50.50), sem = sem(off.per.hr_50.50))

# lifespan data for ancestors
repo.A.ind <- filter(myydf_full, selection == c("Anc")) 
repo.A <- repo.A.ind  %>%  
  group_by(genotype = fct_inorder(genotype)) %>%
   dplyr::summarise(mean = mean(off.per.hr_50.50), sem = sem(off.per.hr_50.50))

## Make figure

# Create x-axis values
x.ind <- c(rep(1,5), rep(3,5), rep(5,5), rep(7,5), 
        rep(9,5), rep(11,5), rep(13,5), rep(15,5))
x <- c(1, 3, 5, 7, 9, 11, 13, 15)

png(filename="~/GitHub/XevoLong/figures/Fig2.png",
    width = 1200, height = 900, res = 96*2)

plot.new()
par(mar = c(7, 7, 5, 7))

plot(jitter(x.ind, amount = 0.5), repo.NL.ind$off.per.hr_50.50, xlim = c(0, 16),
     ylim = c(10, 22), type = "p", pch = 22, bg = "lightblue", 
     col = "lightblue", cex = 0.75, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, lwd = 2, yaxt = "n", xaxt = "n")
box(lwd = 2)

points(jitter(x.ind, amount = 0.5), repo.L.ind$off.per.hr_50.50,
       pch = 22, bg = "pink", col = "pink", lwd = 2, cex = 0.75)

# Add treatment means
points(x, repo.NL$mean, pch = 22, 
      bg = "blue", col = "blue", lwd = 1.25, cex = 2)

points(x, repo.L$mean, pch = 22, 
      bg = "red", col = "red", lwd = 1.25, cex = 2)

# Add error bars
arrows(x0 = x, y0 = repo.NL$mean, 
       y1 = repo.NL$mean + repo.NL$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "blue")

arrows(x0 = x, y0 = repo.NL$mean, 
       y1 = repo.NL$mean - repo.NL$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "blue")

arrows(x0 = x, y0 = repo.L$mean, 
       y1 = repo.L$mean + repo.L$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "red")

arrows(x0 = x, y0 = repo.L$mean, 
       y1 = repo.L$mean - repo.L$sem, 
       angle = 90, length = 0.1, lwd = 2, col = "red")

# Add ancestors means 
segments(x0 = 0.2, y0 = repo.A$mean[1], x1 = 1.8, y1 = repo.A$mean[1], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 2.2, y0 = repo.A$mean[2], x1 = 3.8, y1 = repo.A$mean[2], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 4.2, y0 = repo.A$mean[3], x1 = 5.8, y1 = repo.A$mean[3], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 6.2, y0 = repo.A$mean[4], x1 = 7.8, y1 = repo.A$mean[4], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 8.2, y0 = repo.A$mean[5], x1 = 9.8, y1 = repo.A$mean[5], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 10.2, y0 = repo.A$mean[6], x1 = 11.8, y1 = repo.A$mean[6], col = "black", lty = 3, lwd = 2.5)
segments(x0 = 12.2, y0 = repo.A$mean[7], x1 = 13.8, y1 = repo.A$mean[7], col = "black", lty = 3, lwd = 2.5) 
segments(x0 = 14.2, y0 = repo.A$mean[8], x1 = 15.8, y1 = repo.A$mean[8], col = "black", lty = 3, lwd = 2.5) 

# Add ticks
axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1,
     at = c(1, 3, 5, 7, 9, 11, 13, 15), labels = F)
axis(side = 3, lwd.ticks = 2, cex.axis = 1.25, las = 1,
     at=c(1, 3, 5, 7, 9, 11, 13, 15), labels = F)
axis(side = 2, lwd.ticks = 2, cex.axis = 1.25, las = 1,
    labels = c("10", "15", "20"), at = c(10, 15, 20))
axis(side = 4, lwd.ticks = 2, cex.axis = 1.25, las = 1,
     at=c(10, 15, 20), labels = F)

# Add axis labels
mtext(expression('Strains'), side = 1,
      outer = TRUE, cex = 1.5, line = -2.5, adj = 0.5)

mtext(expression('Reproduction (# d'^-1*')'), side = 2,
      outer = TRUE, cex = 1.5, line = -4, adj = 0.6)
      
# Add legend

legend(0.1, 22, legend = c("no longevity", "longevity"),
       col=c("blue", "red"), pt.bg = c("blue", "red"),
       pch = c(22, 22), pt.cex = 1.5, cex = 1, bty = "n")

# Add strain labels
text(x=0.38, y= 7,"wild type",srt = 60, xpd = NA, cex = 1)
text(x=2.4, y= 7, expression(paste("rpl10a",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=4.4, y= 7, expression(paste("pmr1",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=6.4, y= 7, expression(paste("sch9",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=8.4, y= 7, expression(paste("ypt6",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=10.4, y= 7, expression(paste("tor1",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=12.4, y= 7, expression(paste("tif2",Delta,)), srt = 60, xpd = NA, cex = 1)
text(x=14.4, y= 7, "LYS2", srt = 60, xpd = NA, cex = 1)

# Close Plot Device
dev.off()
graphics.off()

# Show Plot
img <- readPNG("~/GitHub/XevoLong/figures/Fig2.png")

grid.raster(img)

# Statistics

fit.repo <- aov(off.per.hr_50.50 ~ genotype * selection, data = myydf_full)
summary(fit.repo)

#                   Df Sum Sq Mean Sq F value   Pr(>F)    
# genotype            7 170.16   24.31  18.885 2.08e-13 ***
# selection           2 114.86   57.43  44.618 7.35e-13 ***
# genotype:selection 14  54.44    3.89   3.021  0.00132 ** 
# Residuals          64  82.38    1.29                       

# Effect of longevity treatment: decreased reproduction by 2.3 offspring per day d or 13.6%
repo.effect <- myydf_full %>%  
  group_by(selection) %>%
   dplyr::summarise(mean = mean(off.per.hr_50.50), sem = sem(off.per.hr_50.50))
```





















#anc.colors<-c("darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey","darkgrey")

#anc.e0<-c(3.966526375,3.966526375,3.966526375,3.966526375,3.966526375,2.653540408,2.653540408,2.653540408,2.653540408,2.653540408,3.646673218,3.646673218,3.646673218,3.646673218,3.646673218,4.147585939,4.147585939,4.147585939,4.147585939,4.147585939,3.1103613,3.1103613,3.1103613,3.1103613,3.1103613,4.241732325,4.241732325,4.241732325,4.241732325,4.241732325,5.754412658,5.754412658,5.754412658,5.754412658,5.754412658,1.987391586,1.987391586,1.987391586,1.987391586,1.987391586,3.966526375,3.966526375,3.966526375,3.966526375,3.966526375,2.653540408,2.653540408,2.653540408,2.653540408,2.653540408,3.646673218,3.646673218,3.646673218,3.646673218,3.646673218,4.147585939,4.147585939,4.147585939,4.147585939,4.147585939,3.1103613,3.1103613,3.1103613,3.1103613,3.1103613,4.241732325,4.241732325,4.241732325,4.241732325,4.241732325,5.754412658,5.754412658,5.754412658,5.754412658,5.754412658,1.987391586,1.987391586,1.987391586,1.987391586,1.987391586)
```

```{r}

# e0 = life expectancy

xlleg<-readPNG("~/GitHub/XevoLong/figures/20211118_144448_legend_thicker.png")
xllegend<-rasterGrob(xlleg, interpolate = TRUE)

enaught <- ggplot(myydf, aes(x=Strain, y=e0))
enaught +
  #geom_errorbar(aes(ymax=anc.e0,ymin=anc.e0),color=anc.colors,lwd = 2.2,linetype=117) +
  geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.e0,ymax=anc.e0),color=anc.colors,lwd=4.2,linetype=117) +
  geom_jitter(aes(shape = Selection, color = Selection),
              position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),
              size = 6.5, stroke = 2.25,
              show.legend = FALSE
  ) +
  stat_summary(
    aes(color = Selection),
    fun.data = "mean_se", fun.args = list(mult = (1)), #mean_sdl add +/- standard deviation; mult=1 means that it is SD*1 that is drawn.  Mean_se draws the standard error of the mean
    geom = "pointrange", size = 2.25, stroke=2, shape=95,
    position = position_dodge(0.35),
    show.legend=FALSE
  ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nStrain",y="Life expectancy (d)") +
  scale_y_continuous(limits = c(-0.04,16.8),breaks=c(0,3,6,9,12,15), expand = c(0,0)) +
  annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=15.06, ymax=16.5)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))



#anc.reprod<-c(0.293052583,0.293052583,0.293052583,0.293052583,0.293052583,0.26764054,0.26764054,0.26764054,0.26764054,0.26764054,0.21795,0.21795,0.21795,0.21795,0.21795,0.246061944,0.246061944,0.246061944,0.246061944,0.246061944,0.352697718,0.352697718,0.352697718,0.352697718,0.352697718,0.34632925,0.34632925,0.34632925,0.34632925,0.34632925,0.359498994,0.359498994,0.359498994,0.359498994,0.359498994,0.354181633,0.354181633,0.354181633,0.354181633,0.354181633,0.293052583,0.293052583,0.293052583,0.293052583,0.293052583,0.26764054,0.26764054,0.26764054,0.26764054,0.26764054,0.21795,0.21795,0.21795,0.21795,0.21795,0.246061944,0.246061944,0.246061944,0.246061944,0.246061944,0.352697718,0.352697718,0.352697718,0.352697718,0.352697718,0.34632925,0.34632925,0.34632925,0.34632925,0.34632925,0.359498994,0.359498994,0.359498994,0.359498994,0.359498994,0.354181633,0.354181633,0.354181633,0.354181633,0.354181633)


reprod_notmatched <- ggplot(myydf, aes(x=Strain, y=off.per.hr_50.50))
reprod_notmatched +
  #geom_errorbar(aes(ymin=anc.reprod,ymax=anc.reprod),color=anc.colors,lwd = 2.25,linetype=117) +
  geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  geom_jitter(aes(shape = Selection, color = Selection),
              position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.65),
              size = 6.5, stroke = 2.25
  ) +
  stat_summary(
    aes(color = Selection),
    fun.data = "mean_se", fun.args = list(mult = (1)), #mean_sdl add +/- standard deviation; mult=1 means that it is SD*1 that is drawn.  Mean_se draws the standard error of the mean
    geom = "pointrange", size = 2.25, stroke=2, shape=95,
    position = position_dodge(0.35),
    show.legend=FALSE
  ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nStrain",y="No. offspring per hr\n") +
  scale_y_continuous(limits = c(.39,.87),breaks=c(.4,.6,.8), expand = c(0,0)) +
  annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

reprod <- ggplot(myydf, aes(x=Strain, y=off.per.hr.matched))
reprod +
  #geom_errorbar(aes(ymin=anc.reprod,ymax=anc.reprod),color=anc.colors,lwd = 2.25,linetype=117) +
  geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  geom_jitter(aes(shape = Selection, color = Selection),
              position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),
              size = 6.5, stroke = 2.25,
              show.legend=FALSE
  ) +
  stat_summary(
    aes(color = Selection),
    fun.data = "mean_se", fun.args = list(mult = (1)), #mean_sdl add +/- standard deviation; mult=1 means that it is SD*1 that is drawn.  Mean_se draws the standard error of the mean
    geom = "pointrange", size = 2.25, stroke=2, shape=95,
    position = position_dodge(0.35),
    show.legend=FALSE
  ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nStrain",y="No. offspring per hr\n") +
  scale_y_continuous(limits = c(.39,.87),breaks=c(.4,.6,.8), expand = c(0,0)) +
  annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

#Now t-tests for T50 No Long vs. T50 Long life expectancy
var.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$e0),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$e0))
#P = .2344. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$e0),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.01503 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$e0),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$e0))
#P = .7278. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$e0),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.0002782 < 0.001

var.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$e0),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$e0))
#P = .3613. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$e0),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.01071 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$e0),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$e0))
#P = .2920. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$e0),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.01205 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$e0),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$e0))
#P = .1120. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$e0),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.001116 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$e0),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$e0))
#P = .2484. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$e0),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.006902 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$e0),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$e0))
#P = .4977. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$e0),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.01094 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$e0),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$e0))
#P = .2512. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$e0),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)
#p = 0.000668 < 0.001

my.p.vec.e0<-c(t.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$e0),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$e0),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$e0),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$e0),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$e0),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$e0),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$e0),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$e0),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$e0),paired=F,alternative = "greater",mu=0,var.equal=T)$p.value)
print(my.p.vec.e0)

p.adjust(p=my.p.vec.e0, method = "BH")#cite BH&Y 2009
#We now have the following adjusted p-values
#rpl19a:  P = 0.0150 < 0.05
#pmr1:    P = 0.00223 < 0.01
#sch9:    P = 0.0138 < 0.05
#ypt6:    P = 0.0138 < 0.05
#tor1:    P = 0.00298 < 0.01
#tif2:    P = 0.0138 < 0.05
#JD174:   P = 0.0138 < 0.05
#BY4742:  P = 0.00267 < 0.01


#Now t-tests for T46 or 36 No Long vs. T50 Long reproduction rate
var.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$off.per.hr.matched))
#P = .2925. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 3.726EE-6 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$off.per.hr.matched))
#P = .1377. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.03467 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$off.per.hr.matched))
#P = .4903. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.2101 --> n.s.

var.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$off.per.hr.matched))
#P = .0093. Heteroscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=F)
#p = 0.04991 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$off.per.hr.matched))
#P = .9625. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.0006366 < 0.001

var.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$off.per.hr.matched))
#P = .05892. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.007245 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$off.per.hr.matched))
#P = .02214. Heteroscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=F)
#p = 0.001932 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$off.per.hr.matched))
#P = .8486. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.001091 < 0.01

my.p.vec.reprod<-c(t.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=F)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=F)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr.matched),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$off.per.hr.matched),paired=F,alternative = "less",mu=0,var.equal=T)$p.value)

print(my.p.vec.reprod)
p.adjust(p=my.p.vec.reprod, method = "BH")#cite BH&Y 2009
#We now have the following adjusted p-values

#rpl19a:  P = 0.0000298 < 0.001
#pmr1:    P = 0.0462 < 0.05
#sch9:    P = 0.2101 --> n.s.
#ypt6:    P = 0.0570 < 0.1
#tor1:    P = 0.00255 < 0.01
#tif2:    P = 0.0116 < 0.05
#JD174:   P = 0.00386 < 0.01
#BY4742:  P = 0.00291 < 0.01

#Now one-sample t-tests to evaluate the fulfillment of criterion #1.
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p1<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="pmr1")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p2<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="pmr1")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="sch9")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p3<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="sch9")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="ypt6")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p4<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="ypt6")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="tor1")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p5<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="tor1")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="tif2")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p6<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="tif2")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="JD174")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p7<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="JD174")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value
t.test(x=c(filter(myydf, Selection == "Long",Genotype=="BY4742")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)
crit1p8<-t.test(x=c(filter(myydf, Selection == "Long",Genotype=="BY4742")$deltal),y=NULL,alternative = "g",mu=0,paired=F,var.equal=F)$p.value

crit1pvec<-c(crit1p1,crit1p2,crit1p3,crit1p4,crit1p5,crit1p6,crit1p7,crit1p8)
print(crit1pvec)
crit1pvec.adjust<-p.adjust(p=crit1pvec, method = "BH")#cite BH&Y 2009
crit1pvec.adjust
#[1] 0.159380982 0.011749436 0.387123569 0.075379888 0.009069475 0.011749436 0.233487463 0.009069475

#######################################################
#Now t-tests for T50 No Long vs. T50 Long reproduction rate
var.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$off.per.hr_50.50))
#P = .436. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 8.03EE-06 < 0.0001

var.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$off.per.hr_50.50))
#P = .4583. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.07809 < 0.1

var.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$off.per.hr_50.50))
#P = .1775. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.3296 --> n.s.

var.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$off.per.hr_50.50))
#P = .003668. Heteroscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=F)
#p = 0.02674 < 0.05

var.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$off.per.hr_50.50))
#P = .1084. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.008224 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$off.per.hr_50.50))
#P = .0201. Heteroscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=F)
#p = 0.005643 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$off.per.hr_50.50))
#P = .02185. Heteroscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=F)
#p = 0.005708 < 0.01

var.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$off.per.hr_50.50))
#P = .9. Homoscedastic.
t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)
#p = 0.002452 < 0.01

my.p.vec.reprod50.50<-c(t.test(c(filter(myydf, Selection == "Long",Genotype=="rpl19a")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="rpl19a")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="pmr1")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="pmr1")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="sch9")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="sch9")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="ypt6")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="ypt6")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=F)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="tor1")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="tor1")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="tif2")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="JD174")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=F)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr_50.50),c(filter(myydf, Selection == "No Long",Genotype=="BY4742")$off.per.hr_50.50),paired=F,alternative = "less",mu=0,var.equal=T)$p.value)

print(my.p.vec.reprod50.50)
p.adjust(p=my.p.vec.reprod50.50, method = "BH")#cite BH&Y 2009
#We now have the following adjusted p-values
#rpl19a:  P = 0.0000642 < 0.0001
#pmr1:    P = 0.0893 < 0.1
#sch9:    P = 0.330 --> n.s.
#ypt6:    P = 0.0356 < 0.05
#tor1:    P = 0.0132 < 0.05
#tif2:    P = 0.00654 < 0.01
#JD174:   P = 0.0114 < 0.05
#BY4742:  P = 0.00654 < 0.01



###############################################################################
#Now 2-way ANOVAs for all of the measured traits
e02way<-aov(myydf$e0 ~ myydf$Selection + myydf$Genotype + myydf$Selection*myydf$Genotype)
summary(e02way)
#TukeyHSD(e02way)
#Significant effect of selection regime (P = 4.42EE-14)
#Significant effect of strain           (P = 4.01EE-09)
#Significant interaction effect         (P = .00595)

reprod2way<-aov(myydf$off.per.hr.matched ~ myydf$Selection + myydf$Genotype + myydf$Selection*myydf$Genotype)
summary(reprod2way)
#TukeyHSD(reprod2way)

#Significant effect of selection regime (P = 7.48EE-13)
#Significant effect of strain           (P = 1.72EE-12)
#Significant interaction effect      (P = .00399)

reprod2way50.50<-aov(myydf$off.per.hr_50.50 ~ myydf$Selection + myydf$Genotype + myydf$Selection*myydf$Genotype)
summary(reprod2way50.50)
#TukeyHSD(reprod2way50.50)
#Significant effect of selection regime (P = 7.15EE-13)
#Significant effect of strain           (P = 4.95EE-12)
#Significant interaction effect         (P = .00179)


###############################################################################
#Now 2-way ANOVAs for all of the measured traits' DELTA VALUES. Changes vs. the ancor foeach strain
De02way<-aov(myydf$deltal ~ myydf$Selection + myydf$Genotype + myydf$Selection*myydf$Genotype)
summary(De02way)
#TukeyHSD(De02way)
#Significant effect of selection regime (P = 4.42EE-14)
#Significant effect of strain           (P = 5.99EE-12)
#Significant interaction effect         (P = .00595)

Dreprod2way<-aov(myydf$deltar ~ myydf$Selection + myydf$Genotype + myydf$Selection*myydf$Genotype)
summary(Dreprod2way)
#TukeyHSD(Dreprod2way)

#Significant effect of selection regime (P = 7.48EE-13)
#Significant effect of strain           (P = 2.07EE-14)
#No significant interaction effect      (P = .00399)

Dreprod2way50.50<-aov(myydf$deltar.50.50 ~ myydf$Selection + myydf$Genotype + myydf$Selection*myydf$Genotype)
summary(Dreprod2way50.50)
#TukeyHSD(Dreprod2way50.50)
#Significant effect of selection regime (P = 7.15EE-13)
#Significant effect of strain           (P = 4.18EE-16)
#Significant interaction effect         (P = .00179)


#########################################################################################################
#Statistics on strain ancestors

#### THERE'S PROBLEM HERE#####
#First e0. ANOVA among all the strain ancestors
ance0aov<-aov(ance0df$e0 ~ ance0df$strain)
summary(ance0aov)
TukeyHSD(ance0aov)
#No significant differences, P = 0.127 (my favorite number is 127!)

#Second, reproduction rate. ANOVA among all the strain ancestors
ancrraov<-aov(ancrrdf$off.per.hr ~ ancrrdf$Strain)
summary(ancrraov)
TukeyHSD(ancrraov)
#Ssignificant differences, P < 0.05


#########################################################################################################
#Use one-sample t-tests to compare reproduction of 16, 19, and 0 L popns to their ancestors
t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr.matched),alternative = "two.sided",mu=0.681405478)
#p = 0.09747 < 0.05
t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr.matched),alternative = "two.sided",mu=0.706158003)
#p = 0.01377 < 0.05
t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr.matched),alternative = "two.sided",mu=0.694369123)
#p = 0.01829 < 0.05

my.p.vec.reprod.vs.anc.test<-c(t.test(c(filter(myydf, Selection == "Long",Genotype=="tif2")$off.per.hr.matched),alternative = "two.sided",mu=0.681405478)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="JD174")$off.per.hr.matched),alternative = "two.sided",mu=0.706158003)$p.value,t.test(c(filter(myydf, Selection == "Long",Genotype=="BY4742")$off.per.hr.matched),alternative = "two.sided",mu=0.694369123)$p.value)
print(my.p.vec.reprod.vs.anc.test)
p.adjust(p=my.p.vec.reprod.vs.anc.test, method = "BH")#cite BH&Y 2009



################################################################################
#####Bivariate plots: I need to make the bivariate plots that Farrah and Matt were interested in.
rpl19adf<-filter(myydf, Genotype=="rpl19a")
pmr1df<-filter(myydf, Genotype=="pmr1")
sch9df<-filter(myydf, Genotype=="sch9")
ypt6df<-filter(myydf, Genotype=="ypt6")
tor1df<-filter(myydf, Genotype=="tor1")
tif2df<-filter(myydf, Genotype=="tif2")
LYS2df<-filter(myydf, Genotype=="JD174")
WTdf<-filter(myydf, Genotype=="BY4742")

label2<- textGrob(label = "rpl19aΔ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label4<- textGrob(label = "pmr1Δ", x = 0.1, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label5<- textGrob(label = "sch9Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label9<- textGrob(label = "ypt6Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label11<- textGrob(label = "tor1Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label16<- textGrob(label = "tif2Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label19<- textGrob(label = "LYS2", x = 0.1, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label0<- textGrob(label = "WT", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))



rpl19aDbiv <- ggplot(rpl19adf, aes(x=deltar, y=deltal))
rpl19aDbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  #geom_label_repel(label=rpl19a$Selection, nudge_x = 0.02, nudge_y = 1)+
  #geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  #geom_jitter(aes(shape = Selection, color = Selection),position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),size = 6.5, stroke = 2.25,show.legend=TRUE) +
  #stat_summary(aes(color = Selection),fun.data = "mean_se", fun.args = list(mult = (1)),geom = "pointrange", size = 2.25, stroke=2, shape=95, position = position_dodge(0.35),show.legend=FALSE ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.25,.25),breaks=c(-.2,-.1,0,.1,.2), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label2, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  #annotate("text",x=0.68,y=1.5,label="rpl19aΔ",size=12,color="black")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))


pmr1Dbiv <- ggplot(pmr1df, aes(x=deltar, y=deltal))
pmr1Dbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  scale_y_continuous(limits = c(-2.35,2.55),breaks=c(-2,-1,0,1,2), expand = c(0,0)) +
  scale_x_continuous(limits = c(-.08,.16),breaks=c(-.05,0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label4, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

sch9Dbiv <- ggplot(sch9df, aes(x=deltar, y=deltal))
sch9Dbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  scale_x_continuous(limits = c(-.01,.17),breaks=c(0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label5, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

ypt6Dbiv <- ggplot(ypt6df, aes(x=deltar, y=deltal))
ypt6Dbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.01,.17),breaks=c(0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label9, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

tor1Dbiv <- ggplot(tor1df, aes(x=deltar, y=deltal))
tor1Dbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.01,.17),breaks=c(0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label11, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

tif2Dbiv <- ggplot(tif2df, aes(x=deltar, y=deltal))
tif2Dbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.01,.17),breaks=c(0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label16, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

LYS2Dbiv <- ggplot(LYS2df, aes(x=deltar, y=deltal))
LYS2Dbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.01,.17),breaks=c(0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label19, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))


WTDbiv <- ggplot(WTdf, aes(x=deltar, y=deltal))
WTDbiv +
  geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.01,.17),breaks=c(0,.05,.1,.15), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(label0, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))


################################################################################
#####Now plot all 8 strain ancestors together.
ancdf<-filter(myydf_full, Selection=="Anc")
labelanc<- textGrob(label = "Strain ancestors", x = 0.5, y = 0.97,just = c("center", "top"),gp=gpar(col = "#800020",fontsize = 32))

ancbiv <- ggplot(ancdf, aes(x=anc.off.per.hr, y=anc.e0))
ancbiv +
  #geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  geom_label(label=ancdf$Strain, nudge_x = 0.0, nudge_y = 0.00,fontface="bold",size=8.5,fill="white",color="#800020")+
  #geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  #geom_jitter(aes(shape = Selection, color = Selection),position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),size = 6.5, stroke = 2.25,show.legend=TRUE) +
  #stat_summary(aes(color = Selection),fun.data = "mean_se", fun.args = list(mult = (1)),geom = "pointrange", size = 2.25, stroke=2, shape=95, position = position_dodge(0.35),show.legend=FALSE ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nNo. offspring per hr",y="Life expectancy (d)\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(1.75,6.1),breaks=c(2,3,4,5,6), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  annotation_custom(labelanc, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))




################################################################################
#####Now make plots of the avg values of the evolved populations.
#####Bivariate plots: I need to make the bivariate plots that Farrah and Matt were interested in.
rpl19adf<-filter(myydf, Genotype=="rpl19a")
pmr1df<-filter(myydf, Genotype=="pmr1")
sch9df<-filter(myydf, Genotype=="sch9")
ypt6df<-filter(myydf, Genotype=="ypt6")
tor1df<-filter(myydf, Genotype=="tor1")
tif2df<-filter(myydf, Genotype=="tif2")
LYS2df<-filter(myydf, Genotype=="JD174")
WTdf<-filter(myydf, Genotype=="BY4742")

label2<- textGrob(label = "rpl19aΔ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label4<- textGrob(label = "pmr1Δ", x = 0.1, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label5<- textGrob(label = "sch9Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label9<- textGrob(label = "ypt6Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label11<- textGrob(label = "tor1Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label16<- textGrob(label = "tif2Δ", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label19<- textGrob(label = "LYS2", x = 0.1, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))
label0<- textGrob(label = "WT", x = 0.05, y = 0.95,just = c("left", "top"),gp=gpar(col = "black",fontsize = 32))


evoavgdf<-filter(avgdf,Selection!="Anc")
evoavgdf$Selection<-factor(evoavgdf$Selection, levels=c("No Long","Long"))
NLavgdf<-filter(avgdf,Selection=="No Long")
Lavgdf<-filter(avgdf,Selection=="Long")



evoavgcol1<-c("black","black","black","black","black","black","black","black","white","white","white","white","white","white","white","white")
evoavgcol2<-c("white","white","white","white","white","white","white","white","black","black","black","black","black","black","black","black")
evoavgcol3<-c("black","black","black","black","black","black","black","black")
evoavgcol4<-c("white","white","white","white","white","white","white","white")


evoavgDbiv <- ggplot(evoavgdf, aes(x=avg_deltar, y=avg_deltal))
evoavgDbiv +
  #geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  geom_label(label=evoavgdf$Strain, nudge_x = 0.00, nudge_y = 0.0,fontface="bold",size=8.5,color=evoavgcol1,fill=evoavgcol2,segment.size=0)+
  #geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  #geom_jitter(aes(shape = Selection, color = Selection),position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),size = 6.5, stroke = 2.25,show.legend=TRUE) +
  #stat_summary(aes(color = Selection),fun.data = "mean_se", fun.args = list(mult = (1)),geom = "pointrange", size = 2.25, stroke=2, shape=95, position = position_dodge(0.35),show.legend=FALSE ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.25,.25),breaks=c(-.2,-.1,0,.1,.2), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  #annotation_custom(label2, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  #annotate("text",x=0.68,y=1.5,label="rpl19aΔ",size=12,color="black")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

NLavgDbiv <- ggplot(NLavgdf, aes(x=avg_deltar, y=avg_deltal))
NLavgDbiv +
  #geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  geom_label(label=NLavgdf$Strain, nudge_x = 0.00, nudge_y = 0.0,fontface="bold",size=8.5,color=evoavgcol4,fill=evoavgcol3,segment.size=0)+
  #geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  #geom_jitter(aes(shape = Selection, color = Selection),position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),size = 6.5, stroke = 2.25,show.legend=TRUE) +
  #stat_summary(aes(color = Selection),fun.data = "mean_se", fun.args = list(mult = (1)),geom = "pointrange", size = 2.25, stroke=2, shape=95, position = position_dodge(0.35),show.legend=FALSE ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.25,.25),breaks=c(-.2,-.1,0,.1,.2), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  #annotation_custom(label2, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  #annotate("text",x=0.68,y=1.5,label="rpl19aΔ",size=12,color="black")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))

LavgDbiv <- ggplot(Lavgdf, aes(x=avg_deltar, y=avg_deltal))
LavgDbiv +
  #geom_point(aes(shape = Selection, color = Selection),size = 6.5, stroke = 2.25) + # Show dots
  geom_label(label=Lavgdf$Strain, nudge_x = 0.00, nudge_y = 0.0,fontface="bold",size=8.5,color=evoavgcol3,fill=evoavgcol4,segment.size=0)+
  #geom_errorbar(data=myydf, mapping = aes(x=Strain,ymin=anc.off.per.hr,ymax=anc.off.per.hr),color=anc.colors,lwd=4.2,linetype=117) +
  #geom_jitter(aes(shape = Selection, color = Selection),position = position_jitterdodge(jitter.width = 0.6, dodge.width = 0.55),size = 6.5, stroke = 2.25,show.legend=TRUE) +
  #stat_summary(aes(color = Selection),fun.data = "mean_se", fun.args = list(mult = (1)),geom = "pointrange", size = 2.25, stroke=2, shape=95, position = position_dodge(0.35),show.legend=FALSE ) +
  scale_color_manual(values = c("black","black"), labels = c("No Long","Long")) +
  scale_shape_manual(values = c(15,0), labels = c("No Long", "Long")) +#12 is a square with a vertical cross inside it
  labs(x="\nΔR",y="ΔL\n") +
  #scale_y_continuous(limits = c(-3.75,3.75),breaks=c(-3,-2,-1,0,1,2,3), expand = c(0,0)) +
  #scale_x_continuous(limits = c(-.25,.25),breaks=c(-.2,-.1,0,.1,.2), expand = c(0,0)) +
  #annotation_custom(grob = xllegend, xmin=7.4, xmax=8.4, ymin=.82, ymax=.865)+
  #annotation_custom(label2, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf)+
  #annotate("text",x=0.68,y=1.5,label="rpl19aΔ",size=12,color="black")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black")) +
  theme(legend.key=element_blank(),axis.text.x=element_text(size=34,margin = margin(t = 20, r = 0, b = 0, l = 0)),axis.text.y=element_text(size=34,margin = margin(t = 0, r = 20, b = 0, l = 0)),axis.title=element_text(size=36),legend.text=element_text(size=22),legend.title = element_text(size=34), axis.ticks.y = element_line(color = "black", size = 3), axis.ticks.x = element_line(color = "black", size = 3), axis.ticks.length.x=unit(0.7, "cm"),axis.ticks.length.y=unit(0.7, "cm"), legend.position = "none", panel.border = element_rect(color = "black", fill = NA, size = 3.5), axis.line = element_line(colour = "black"))